Developing a preprint culture in biology

### 2012-09-28 ms.tex
editing arxiv section

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

The review process as a whole is critically over-loaded, because the number of
active scientists increases, because the pressure to publish increases, and
because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  At
the same times, rejection rates are high in most journals (REF), and when not
invited to submit a revisions, authors must start the whole process all over
again. It's thus no surprise that different initiatives emerged over the last
few years, to decrease the time spent in review. XXX et coll. (REF) called for
the recycling and reuse of peer-reviews: by attaching previous reviews, and
detailed replies, to a new submission, both the editor and the referees can
gauge the work done on the manuscript, and perhaps evaluate it with less
prejudice. In a similar way, the \emph{Peerage of Science} initiative allows
authors to seek anonymous pre-review by their peers. Some journals now accept to
publish papers which received good evaluations, with \emph{Animal Biology}
having recently accepted first a paper reviewed entirely with the \emph{Peerage of
Science} \cite{abb12}, effectively outsourcing the review process. A widespread
use of preprint servers can achieve the same goal of reducing the time spent in
review. By putting a manuscript for open comments and criticisms, the authors
will receive valuable feedback and can improve the version which will be
submitted. With a rich enough community of scientists depositing preprints, and
commenting on them, the process of an open pre-review can become widespread and
will overall increase the quality of first submissions.

\begin{figure}[ht!] \centering\includegraphics[width=0.50\textwidth]{map.pdf}
\caption { It can take several months, and even a few years, before a submitted
paper is officially published and citable.  The average time to publication
varies greatly between journals and can be as low as 104 days (Evolution for
2011) to 213 (PLOS One in 2010).  Meanwhile, few people are aware of the
research that has been done since, typically, only close colleagues are given
access to the preprints. With public preprint servers, the science is
immediately available and can be openly discussed, analysed, and integrated into
current research. It benefits both science and publishers. Both want the papers
to be well-known and cited, and public preprints make it possible to integrate
research even before publication, greatly improving immediacy.  }
\label{fig:map} \end{figure}

@@

Some of the responses to public preprints are surprising since they are,
essentially, the same as exchanging preprints among colleagues.  Prepublication
reviews by a small network of colleagues is an important part of the scientific
process, which is attested by the fact that nearly all published papers
acknowledge comments by people not listed as co-authors.  Preprint servers
simply offer a way to extend this network of colleagues to the entire scientific
community. It ensures that science is not constrained by small networks of
scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
democratic reasons: he wanted everyone from students in small universities to
Ivy-League professors to have access to the most recent scientific \emph{ideas}.
Ginsparg's revolutionary idea was simply to use the power of the internet for
preprints, not just for the end product, so the process can be open from A to Z,
instead of being just open at the end of the process.

@@

% Not sure about this paragraph, as much as I love to hate MS Office, I would
% rather keep the thing as a "pro-preprint" paper only and not use it to promote
% LaTeX/R.
% -- PhDP
There are other barriers to adoption of preprint servers by biologists.  The
most notable preprint server, arXiv, is designed to work best with \LaTeX, the
dominant document preparation system among physicists and mathematicians.
Jackson \cite{jackson2002preprints} argues that \LaTeX introduced an
open source mindset to its users, who now freely share their research
findings as well as their software.  Many biologists instead use proprietary
software to prepare their research findings, and many journals officially prefer
Microsoft Word documents as submissions.  The recent discipline-wide adoption of
free software packages such as R and associated document generation systems
\cite{xie2012}, as well as interest in open access publishing, has coincided
with recent rise in use of preprint servers by biologists, supporting Jackson's
claims \cite{xie12}.

@@

arXiv (\url{http://arxiv.org/}) is the most widely-used preprint server today,
and its use is almost universal in mathematics and most branches of physics.
Physicist Paul Ginsparg originated arXiv in 1991 for theoretical high-energy
physicists to communicate preprints via email and ftp, and soon thereafter
adopted the newly created world-wide web\cite{jackson2002preprints}.  arXiv now
receives over 7,000 submissions per month
(\url{http://arxiv.org/show_monthly_submissions}).  arXiv divides its
submissions into subcategories of physics, mathematics, computer science,
quantitative biology, finance and statistics.  The quantitative biology category
includes subcategories for Populations and Evolution, Quantitative Methods and
other categories that may be of interest to biologists.

Submission to arXiv is fully automated via the world-wide web.  Authors can
submit \TeX/\LaTeX documents that are compiled on the server, or directly submit
in PDF/PS format (for example, as exported by a word processor).  A moderation
system was put in place in 2004: papers must be categorized by an ``endorser.''
At least one author of a paper must be an endorser that has previously submitted
a paper or has received permission to submit to a particular category.  Many
authors in mathematics and physics submit papers as soon as they are ready for
review by colleagues, although another popular option is submitting
simultaneously to a journal and arXiv.

Most papers posted to arXiv are eventually printed in journals.  There are
notable exceptions, including Perelman's landmark paper leading to the proof of
the Poincar\'{e} conjecture \cite{2002math.....11159P}.  arXiv provides a
reliable citation system for all eprints (see our citation
\cite{2002math.....11159P}), lending a form of ``intellectual priority'' to
works posted there.  Despite these marks of arXiv functioning as a scientific
journal, arXiv has never sought to replace scientific journals and explicitly
states that it serves a different function as ``an openly accessible, moderated
repository for scholarly articles in specific scientific disciplines.''

arXiv is now administered by the Cornell University Libraries.  Funding comes
from voluntary pledges by academic institutions along with matching funds from
the Simons Foundation \cite{arxiv_future}.  One-hundred twenty six of the top
two-hundred institutions in terms of downloads have provided the operating
budget for arXiv over the next five years.  This plan reduces the financial
burden on Cornell University and transfers governance to a collaborative
community in accordance with arXiv's key principles.  arXiv takes numerous
measures to ensure that the repository will remain permanently available and
submissions will be readable.

>>>>

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

Furthermore, the review process as a whole is critically over-loaded, because
the number of active scientists increases, because the pressure to publish
increases, and because of an effect dubbed ``the tragedy of the reviewers
commons'' REF.  At the same times, rejection rates are high in most journals
(REF), and when not invited to submit a revision, authors must start the whole
process all over again. It's thus no surprise that different initiatives emerged
over the last few years to decrease the time spent in review. XXX et coll.
(REF) called for the recycling and reuse of peer-reviews: by attaching previous
reviews and detailed replies to a new submission, both the editor and the
referees can gauge the work done on the manuscript, and perhaps evaluate it with
less prejudice. In a similar way, the \emph{Peerage of Science} initiative
allows authors to seek anonymous pre-review by their peers. Some journals now
accept to publish papers which received good evaluations, with \emph{Animal
Biology} having recently accepted first a paper reviewed entirely with the
\emph{Peerage of Science} \cite{abb12}, effectively outsourcing the review
process. A widespread use of preprint servers can achieve the same goal of
reducing the time spent in review. By putting a manuscript for open comments and
criticisms, the authors will receive valuable feedback and can improve the
version which will be submitted. With a rich enough community of scientists
depositing preprints, and commenting on them, the process of an open pre-review
can become widespread and will overall increase the quality of first
submissions.

\begin{figure}[ht!] \centering\includegraphics[width=0.50\textwidth]{map.pdf}
\caption { It can take several months, and even a few years, before a submitted
paper is officially published and citable.  The average time to publication
varies greatly between journals and can be as low as 104 days (Evolution for
2011) to 213 (PLOS One in 2010).  Meanwhile, few people are aware of the
research that has been done since, typically, only close colleagues are given
access to the preprints. With public preprint servers, the science is
immediately available and can be openly discussed, analyzed, and integrated into
current research. It benefits both science and publishers. Both want the papers
to be well-known and cited, and public preprints make it possible to integrate
research even before publication, greatly improving immediacy.  }
\label{fig:map} \end{figure}

@@

Prepublication reviews by a small network of colleagues is an important part of
the scientific process, which is attested by the fact that nearly all published
papers acknowledge comments by people not listed as co-authors.  Preprint
servers simply offer a way to extend this network of colleagues to the entire
scientific community. It ensures that science is not constrained by small
networks of scientists exchanging ideas.  Paul Ginsparg created arXiv.org in
part for democratic reasons: he wanted everyone from students in small
universities to Ivy-League professors to have access to the most recent
scientific \emph{ideas}.  Ginsparg's revolutionary idea was simply to use the
power of the internet for preprints, not just for the end product, so the
scientific process can be open as soon as possible.

@@

% Not sure about this paragraph, as much as I love to hate MS Office, I would
% rather keep the thing as a "pro-preprint" paper only and not use it to promote
% LaTeX/R.
% -- PhDP

%There are other barriers to adoption of preprint servers by biologists.  The
%most notable preprint server, arXiv, is designed to work best with \LaTeX, the
%dominant document preparation system among physicists and mathematicians.
%Jackson \cite{jackson2002preprints} argues that \LaTeX introduced an
%open source mindset to its users, who now freely share their research
%findings as well as their software.  Many biologists instead use proprietary
%software to prepare their research findings, and many journals officially prefer
%Microsoft Word documents as submissions.  The recent discipline-wide adoption of
%free software packages such as R and associated document generation systems
%\cite{xie2012}, as well as interest in open access publishing, has coincided
%with recent rise in use of preprint servers by biologists, supporting Jackson's
%claims \cite{xie12}.

@@

arXiv (\url{http://arxiv.org/}) is the most widely-used preprint server today,
and its use is almost universal in some branches of mathematics and physics.  It
provides a reliable citation system for all eprints and is especially popular in
high-energy physics. Physicist Paul Ginsparg created arXiv in 1991 for
theoretical high-energy physicists to communicate preprints via email and ftp,
and soon thereafter adopted the newly created world-wide
web\cite{jackson2002preprints}.  arXiv now receives over 7,000 submissions per
month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
submissions into subcategories of physics, mathematics, computer science,
quantitative biology, finance and statistics.  The quantitative biology category
includes subcategories for Populations and Evolution, Quantitative Methods and
other categories that may be of interest to biologists.

Submission to arXiv is fully automated.  Authors can submit \TeX/\LaTeX
documents that are compiled on the server or directly submit in PDF/PS format
(for example, as exported by a word processor).  A moderation system was put in
place in 2004: papers must be categorized by an endorser. At least one
author of a paper must be an endorser that has previously submitted a paper or
has received permission to submit to a particular category.  Many authors in
mathematics and physics submit papers as soon as they are ready for review by
colleagues, although another popular option is submitting simultaneously to a
journal and arXiv.

Most papers posted to arXiv are eventually printed in journals but there are
notable exceptions, such as Perelman's landmark paper leading to the proof of
the Poincar\'{e} conjecture \cite{2002math.....11159P}. Yet, arXiv has never
sought to replace scientific journals and explicitly states that it serves a
different function as ``an openly accessible, moderated repository for scholarly
articles in specific scientific disciplines.'' arXiv is now administered by the
Cornell University Libraries, with funding coming from voluntary pledges by academic
institutions along with matching funds from the Simons Foundation
\cite{arxiv_future}.  One-hundred twenty six of the top two-hundred institutions
in terms of downloads have provided the operating budget for arXiv over the next
five years.  This plan reduces the financial burden on Cornell University and
transfers governance to a collaborative community in accordance with arXiv's key
principles.  arXiv takes numerous measures to ensure that the repository will
remain permanently available and submissions will be readable.
